A Horrocks-type theorem for even orthogonal $K_2$

### 2020-10-21 dl-paper.tex
Fix compilation
Fix display formulas

\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\Img}{Im}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\HH}{H}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\KO}{KO}
\DeclareMathOperator{\GW}{GW}
\DeclareMathOperator{\colim}{colim}
\newcommand{\inv}{^{-1}}

@@

\begin{rem} It is possible to give a different proof of the above lemma in the case $\Phi = \rC_\ell$ for $\ell \geq 5$ under the additional assumption that the characteristic of $k$ is not $2$. Indeed, we have the following chain of isomorphisms:
\begin{multline} \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \\ \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\end{multline}
in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the unstable case. \end{rem}

@@

For the rest of this subsection $M$ is the maximal ideal $A$.
We denote by $\beta$ another fixed root of $\Phi$ forming an acute angle with $\alpha$ (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df}\label{def:Kab} 
Fix a root $\delta \in \Phi \setminus \Psi$. Define $\widetilde{K}(\alpha, \beta)$ as the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parameterized by $\xi \in A[X]$, $f\in M[X]$:
 \begin{enumerate}[label=(K\arabic*)]
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\delta}(f, X\xi)$. \end{enumerate} \end{df}
\begin{prop} \label{K-a-b} One has \[K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X).\] 
\end{prop} 
\begin{proof}
It is clear that $K(A[X], M[X]) \supseteq \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X)$. Let us prove the reverse inclusion. Fix an element $g\in K(A[X], M[X])$. We need to show that $g$ lies in the specified product of subgroups.

@@

 Let $a$ and $b$ be elements of $A$ and $(g, h, u)$ be an element of $V$.
 By the first part of the proof of~\cref{lem:orbit-action} we may assume that $p(g,h,u)\in P_\alpha(m)$ for some $m \in M$.
 From~\eqref{T_1} we obtain that 
 \begin{multline}\label{add-computation}
  T_\alpha(bX^{-1}) \cdot T_\alpha(aX^{-1}) (g, [h], u) = \\ = T_\alpha(bX^{-1}) \cdot \left(x_\alpha(aX^{-1})\cdot g ,\ \left[ h' \right],\ u \cdot (1 + am)\right),
 \end{multline}
 where $h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)$.
 Notice that we can not invoke~\eqref{T_1} for the second time because the value of the function $p$ on the triple $(x_\alpha(aX^{-1})\cdot g ,\ h',\ u \cdot (1 + am))$ does not belong to $P_\alpha(*)$.

>>>>

\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\Img}{Im}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\HH}{H}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\GG}{G}
\DeclareMathOperator{\KO}{KO}
\DeclareMathOperator{\GW}{GW}
\DeclareMathOperator{\colim}{colim}
\newcommand{\inv}{^{-1}}

@@

\begin{rem} It is possible to give a different proof of the above lemma in the case $\Phi = \rC_\ell$ for $\ell \geq 5$ under the additional assumption that the characteristic of $k$ is not $2$. Indeed, we have the following chain of isomorphisms:
\begin{equation} \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\end{equation}
in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the unstable case. \end{rem}

@@

For the rest of this subsection $M$ is the maximal ideal $A$.
We denote by $\beta$ another fixed root of $\Phi$ forming an acute angle with $\alpha$ (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df}\label{def:Kab} 
Fix a root $\delta \in \Phi \setminus \Psi$. Define $\widetilde{K}(\alpha, \beta)$ as the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parameterized by $\xi \in A[X]$, $f\in M[X]$:
 \begin{enumerate}[label=(K\arabic*)]
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\delta}(f, X\xi)$. \end{enumerate} \end{df}
\begin{prop} \label{K-a-b} One has $K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X).$
\end{prop} 
\begin{proof}
It is clear that $K(A[X], M[X]) \supseteq \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X)$. Let us prove the reverse inclusion. Fix an element $g\in K(A[X], M[X])$. We need to show that $g$ lies in the specified product of subgroups.

@@

 Let $a$ and $b$ be elements of $A$ and $(g, h, u)$ be an element of $V$.
 By the first part of the proof of~\cref{lem:orbit-action} we may assume that $p(g,h,u)\in P_\alpha(m)$ for some $m \in M$.
 From~\eqref{T_1} we obtain that 
 \begin{equation}\label{add-computation}
  T_\alpha(bX^{-1}) \cdot T_\alpha(aX^{-1}) (g, [h], u) = T_\alpha(bX^{-1}) \cdot \left(x_\alpha(aX^{-1})\cdot g ,\ \left[ h' \right],\ u \cdot (1 + am)\right),
 \end{equation}
 where $h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)$.
 Notice that we can not invoke~\eqref{T_1} for the second time because the value of the function $p$ on the triple $(x_\alpha(aX^{-1})\cdot g ,\ h',\ u \cdot (1 + am))$ does not belong to $P_\alpha(*)$.
